\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scale=0.9, top=1.5cm, bottom=1.5cm, left=2cm, right=2cm]{geometry}

% https://tug.org/FontCatalogue/sansseriffonts.html
\usepackage[sfdefault,light]{FiraSans}
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}

%----------------------------------------------------------------------------

% Colors
\definecolor{goodgreen}{HTML}{00ab44}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% Section Formatting
\titleformat{\section}{\Large\scshape\raggedright\color{goodgreen}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\newcolumntype{C}{>{\centering\arraybackslash}X} 

\newenvironment{joblong}[2]
    {
    \par\vspace{4pt}\noindent
    \begin{tabularx}{\linewidth}{@{} X r @{}}
    \textbf{#1} & #2 \\
    \end{tabularx}
    \vspace{-8pt}
    \begin{itemize}[nosep, leftmargin=1.5em, itemsep=2pt, label=--]
    }
    {
    \end{itemize}
    \vspace{4pt}
    }


%----------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} % No page numbers


%----------------------------------------------------------------------------
\begin{center}
    {\Huge \textbf{Logan Shehane}}\\[8pt]
    \href{https://github.com/SentientDragon5}{\faGithub\ SentientDragon5} \ $|$ \ 
    \href{https://linkedin.com/in/lashehane/}{\faLinkedin\ lashehane} \ $|$ \ 
    \href{https://sentientdragon5gamedev.itch.io}{\faGamepad\ Demos} \ $|$ \ 
    \href{mailto:lashehane@outlook.com}{\faEnvelope\ lashehane@outlook.com}
\end{center}

%----------------------------------------------------------------------------
\section{Summary}
\noindent
Software Engineer with experience in full-stack software development and User Experience Development. Full-time student at UCSC with plans to pursue a Masters in Human Computer Interaction or Computer Science. Successfully developed and published multiple tech demos and a complete game.


%----------------------------------------------------------------------------
\section{Education}
\noindent
\begin{tabularx}{\linewidth}{@{} X r @{}}     
\textbf{B.S. Computer Science: Game Design at UC Santa Cruz} (GPA: 3.93) & Sept 2022 - June 2026 \\
\end{tabularx}
\vspace{-6pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=2pt, label=--]
    \item Focused on Capstone Game Project, Procedural Generation, AI, and LLMs
    \item Possess well-rounded knowledge in a variety of topics including Sailing, Paleontology, Music
\end{itemize}

%----------------------------------------------------------------------------
\section{Experience}

\begin{joblong}{Software Development Intern -- Guide Robotics (Tokyo, Japan)}{June 2025 - Aug 2025}
    \item Configured ROS and Gazebo environments to simulate a TurtleBot 4, successfully integrating both the digital twin and physical robot with internal software tools.
    \item Researched and implemented a YOLO-based computer vision model for object identification on a Qualcomm RB3 Gen 2 Development Kit.
\end{joblong}

\begin{joblong}{Software Researcher -- UCSC Procedural Generation Lab}{Sept 2024 - June 2025}
    \item Programmed scripts to generate procedural worlds using algorithms like Wave Function Collapse.
    \item Compiled several datasets for use in training Large Language Models and fine-tuned LLMs.
    \item Co-authored a confrence paper published at FDG, contributing to research and technical details.
\end{joblong}

\begin{joblong}{Tutor and Grader -- UCSC Baskin School of Engineering}{Sept 2024 - June 2025}
    \item Conducted weekly meetings with students to instruct on the use of 3D modeling software.
    \item Developed teaching materials, graded work, and provided feedback to students.
\end{joblong}

\begin{joblong}{Independent Contractor -- Turbostrat LLC}{Mar 2024 - Apr 2024}
    \item Designed an interactive UI and tutorial for mobile AR game.
    \item Planned, implemented, and documented software and design.
\end{joblong}

\begin{joblong}{Robotics Club Team Lead -- UCSC Slugbotics Arm Team}{Sept 2023 - June 2025}
    \item Engineered an open-source robotic arm; maintained and expanded the codebase.
    \item Organized meetings, demonstrated progress, and onboarded new members.
\end{joblong}

\begin{joblong}{Rocket Team Contributor -- UCSC Rocket Team (Thrust Vector Control)}{Sept 2024 - June 2025}
    \item Developed applications utilizing Satellite APIs and OpenCV computer vision to compare live camera feeds and identify suitable landing locations for a moving rocket.
    \item Conducted research and CAD for hardware components including the camera and mount.
\end{joblong}

%----------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{} l X @{}}
\textbf{Languages} & Python, C\# (Unity), C, C++, Javascript, HTML, CSS \\ [4pt]
\textbf{Technologies} & Unity, Godot, Blender 3D, LLMs, APIs, Git, Unix, ROS2, Gazebo, OpenCV, YOLO, RVis \\ [4pt]
\textbf{Awards} & Dean's Honors, Eagle Scout
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today \ $|$ \ \href{https://sentientdragon5.github.io/Resume/}{Open Latest}}

\enlargethispage{2\baselineskip}
\end{document}